Quality Criteria for SKOS Vocabularies

### 2012-03-21 criteria.tex
changed qc1

SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag. This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} or \texttt{skos:documentation}. Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags by iterating over concepts \todo{not resources? any resource can have a prefLabel, right? and prefLabel has no domain specified} in $C$ and collect those that have relations to plain literals without or with invalid language tags. We check the validity of a language tag by comparing it to the list of tags defined in \todo{CM}{??}.\todo{CM}{is there any literature reference for this criterion?}

>>>>

SKOS defines a set of properties that link resources with RDF Literals, which are plain text natural language strings with an optional language tag. This includes the labeling properties \texttt{skos:prefLabel}, \texttt{skos:altLabel}, \texttt{skos:hiddenLabel} and also SKOS documentation properties, such as \texttt{skos:note} and subproperties thereof. Since omitting language tags or using non-standardized, private language tags in a SKOS vocabulary could limit language-dependent structural queries, we check a SKOS vocabulary for omitted language tags by iterating over resources in $IR$ and collect those that have relations to plain literals without or with invalid language tags. We delegate validity checking of language tags to methods provided by the by OpenRDF\footnote{\url{http://www.openrdf.org/}} framework that in turn checks for conformance with RFC3066\footnote{\url{http://www.ietf.org/rfc/rfc3066.txt}}.\todo{CM}{is there any literature reference for this criterion?}
